\documentclass[a4paper, oneside, final, 10pt]{scrartcl}
\usepackage{myCV}
%\usepackage{garamondx}
\authorslist{M.~Hilton}

\begin{document}

\name{Michael Hilton}
\address{School of Electrical Engineering \& Computer Science\\
         Oregon State University\\
         Corvallis, Oregon 97331 }
        {\phone{+1 (619) 933-3451} \\
         \email{hiltonm@eecs.oregonstate.edu} \\
         \web{web.engr.oregonstate.edu/$\sim$hiltonm} }
\rule{\textwidth}{1pt}

\section{Research Interests}

\section{Education}

\entry{\textit{Doctor of Philosophy}, Computer Science \\ 
Oregon State University, Corvallis, Oregon \hfill Fall 2013 -- Present \\ 
Concentration: Software Engineering, Advisor: Dr Danny Dig } 

\entry{\textit{Master of Science}, Computer Science \\ 
California Polytechnic State University, San Luis Obispo, California \hfill Winter 2013 \\
Advisor: Dr David Janzen }

\entry{\textit{Bachelor of Science}, Computer Science \\ 
San Diego State University, San Diego, California	 \hfill Spring 2002 \\
}

\entry{\textit{Associate of Science}, Computer Information Systems \\ 
Grossmont Community College, El Cajon, California \hfill Spring 1999 \\
}


\section{Teaching Experience}

\entry{\textit{CS361 Software Engineering I	} \\
Instructor of Record. Oregon State  \hfill Winter 2016 \\
}

\entry{\textit{CSC/CPE 101 Fundamentals of Computer Science I} \\
Instructor of Record. Cal Poly San Luis Obispo  \hfill Spring 2013 \\
}


\section{Professional Experience}


\entry{\textit{Software Engineer/Scientist} \\
Space and Naval Warfare Systems Center - Pacific,  \hfill June 2002 -- August 2011 \\
San Diego, CA
}

\entry{\textbf{Team Lead White House Situation Room Upgrade Project}}
\begin{itemize}
  \item Team lead for Server portion of White House Situation Room Upgrade Project.
  \item Responsible for Server team development effort in ASP.NET using C\#. Also responsible for scheduling, resource management, and interfacing with Client team. 
  \item Responsible for managing and mentoring new hires 
\end{itemize}

\entry{\textbf{Lead Software Engineer}}
\begin{itemize}
  \item Lead Engineer for a Navy Sponsored Web Based Data Aggregation Project consisting of 6 Government and Contractor Engineers.  Responsible for tasking engineering team, monitoring progress, and overseeing new features. Also, meeting with client, and helping them develop requirements for project.  
  \item Promoted best practices in team, including following guidelines for successful meetings in order to make team meetings more efficient and productive. 
  \item Implemented source control for project to better manage software changes and versions.
  \item Responsible for briefing VIPs, including US Navy Admirals.
  \item Chosen to be a member of Cyber-Warfare Strategy Planning meeting, which was comprised of senior leadership and outstanding engineers.
\end{itemize}

\entry{\textbf{Software Engineer}}
\begin{itemize}
  \item Primary Software Engineer for two projects starting with developing a demo from a concept, lead engineer for lifetime of the development cycle, including transition period once project was finished and delivered
  \item Developed Embedded Application running on windows mobile in embedded Visual Basic and embedded C++ deployed and used by USN and US Coast Guard.
\end{itemize}


\nocite{*}
\bibliography{publications}
\bibliographystyle{ieeetr}
\vspace{3pt}
%\endgroup

%\section{Memberships}
%
%\entry{\textit{Student Member}, Association for Computing Machinery (ACM) \hfill 2013 -- Present}

\section{Honors}

\entry{\textit{Distinguished Paper Awards}
Awarded to the top papers at a conference. Received at FSE 2016.}

\entry{\textit{J.L. Moore Doctoral Fellowship}
Awarded to Cal Poly CSC graduates who persue Doctoral Studies in Computer Science. Received 2013,2014,2015}



\section{Service}

\entry{\textit{Instructor}, CS/ECE507 Graduate Seminar (Introduction to Grad School)  	\hfill Fall 2016}

\entry{\textit{Video Chair}, ACM SIGPLAN conference on Systems, Programming, Languages and Applications: Software for Humanity (SPLASH) 	\hfill 2016}

\entry{\textit{Student Volunteer}, International Conference on Software Engineering (ICSE)	\hfill 2016}

\entry{\textit{Video Chair}, ACM SIGPLAN conference on Systems, Programming, Languages and Applications: Software for Humanity (SPLASH) 	\hfill 2015}

\entry{\textit{Student Volunteer}, ACM SIGPLAN conference on Systems, Programming, Languages and Applications: Software for Humanity (SPLASH) 	\hfill 2014}

\entry{Journal Review??}


%\entry{\textit{Steward}, Coalition of Graduate Employees Local 6069 (AFT, AFL-CIO) \hfill September 2016 -- Present}
%
%\entry{\textit{Reviewer}, 30th IEEE/ACM International Conference on Automated Software Engineering
%(ASE) \hfill 2015}

\end{document}
